A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-13 docs/icccn2009/paper.tex
Revised background section
git-svn-id: svn://localhost/netbeams/trunk@372 559edde2-a4d4-44e0-96fc-4035e40d7396

Researchers in the geosciences rely on sensor data collected by highly
specialized sensors such as the Seabird or YSI. These sensors are
usually deployed in remote locations that not only make their
maintenance difficult, but also access to their measurements.
Typically, the sensors are autonomous in the sense that they can run
for a certain time on battery power and store the measurement data in
internal memory. Only when the sensors are serviced, the measurement
data, which was collected since the last servicing, is uploaded to a 
portable storage device. From there, the data can be uploaded to
server. Notice that this manual procedure to retrieve sensor data is not only
error prone, but also results are in a serious time lag between the time
the sensor performs the measurement and when it becomes available for
further processing. For many applications, however, it would be beneficial to
have near-realtime access to the sensor measurement. In this way, being able 
to access data when they become available on the sensor device would also
reduce the maintenance overhead.

---

The YSI 6600EDS V2 Sonde \cite{Sonde01} is a water quality monitoring device that
gathers water quality data, and operates in fresh, sea, or polluted
water. Some of the measurements that the YSI is capable of are
conductivity, temperature, chloride, ammonium, nitrate, turbidity, and
chlorophyll.  It is under 55 cm in length, 8.9 cm in diameter, and
weighs approximately 3.18 kg. It operates at temperatures between -5
to +50 deg C and at depths up to 200 meters.  It uses 8 C-size
Alkaline Batteries or External 12 VDC. Battery life can last up to 75
days depending on sensor configuration. The Sonde's bulkhead contains
multiple pin connectors to support sensor probes for measuring the
following:

@@

---

Start with some related work. Who else has done an OSGi-based
infrastructure for sensor networks? Kleber: I believe you have a few
references. This section should be a combination of a use case (using
the RTC and their YSI sonde as an example) and a requirements
analysis: requirements such as remote management and monitoring
capabilities, time-delayed communication, etc. In this section should
be no mentioning of DSP. Length: 1 page.

@@

\begin{figure}[!htb]
\centering
%\epsfig{file=dsp-messages-container, width=8cm}
\caption{\label{FIG_DSP_MSGS_CONTAINER} The structure of Messages Container.}
\end{figure}

>>>>

Environmental researchers typically use standard, off-the-shelf
sensing devices for their purposes. These sensing devices are at the
opposite spectrum of miniature sensors such as SmartDust. One such
device is the YSI 6600EDS V2 Sonde \cite{Sonde01}. It is a water
quality monitoring device that gathers water quality data, and
operates in fresh, sea, or polluted water. Some of the measurements
that the YSI is capable of are conductivity, temperature, chloride,
ammonium, nitrate, turbidity, and chlorophyll.  It is under 55 cm in
length, 8.9 cm in diameter, and weighs approximately 3.18 kg. It
operates at temperatures between -5 to +50 deg C and at depths up to
200 meters.  It uses 8 C-size Alkaline Batteries or External 12 VDC.
Battery life can last up to 75 days depending on sensor configuration.
The Sonde's bulkhead contains multiple pin connectors to support
sensor probes for measuring parameters as shown in Table
\ref{TAB_SONDE_MEASUREMENTS}.

@@

We provide these details to show that sensing devices such as the YSI
are highly specialized devices with a unit price of several thousand
dollars. These sensors are usually sparsely deployed in remote
locations that not only make their maintenance difficult, but also
access to their measurements.  Typically, the sensors are autonomous
in the sense that they can run for a certain time on battery power and
store the measurement data in internal memory. Only when the sensors
are serviced, the measurement data, which was collected since the last
servicing, is uploaded to a portable storage device. From there, the
data can be uploaded to server. This manual procedure to retrieve
sensor data is not only error prone, but also results are in a serious
time lag between the time the sensor performs the measurement and when
it becomes available for further processing. For many applications,
however, it would be beneficial to have near-realtime access to the
sensor measurement. We identify the following requirements that an
end-to-end infrastructure supporting devices such as the YSI should
offer:

\begin{itemize}
\item Allow near-realtime access to sensor measurements.
\item Allow remote servicing that include changing of configuration
  parameters as well as software upgrades.
\item Support cost-effective long distance communication link.
\item Can be deployed in remote locations in unprotected outdoor
  conditions.
\end{itemize}

In the next section we describe a software architecture that provides
a foundation to fulfill these requirements.

@@

\begin{figure}[!htb]
\centering
\epsfig{file=dsp-messages-container, width=8cm}
\caption{\label{FIG_DSP_MSGS_CONTAINER} The structure of Messages Container.}
\end{figure}
